Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis

### 2021-08-17 analysis/chapters/paper_ana_20181122.tex
Enviado al resto de los autores

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Impact of frequent assimilation of surface and satellite observations in an MCS case during RELAMPAGO field campaign. Part I: impact on the analysis},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Impact of frequent assimilation of surface and satellite observations in an MCS case during RELAMPAGO field campaign. Part I: impact on the analysis}
    \author[UBA,CIMA,CNRS]{Paola Belén Corrales\corref{1}}
   \ead{paola.corrales@cima.fcen.uba.ar} 
    \author[UBA,CIMA,CNRS]{Victoria Galligani}

@@

  \begin{abstract}
  The impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF is evaluated. We conducted a case study corresponding to a huge mesoscale convective system (MCS) developed over central and north-eastern Argentina during November 22, 2018. The accumulated precipitation observed during the transit of the MCS was quite high, exceeding 200 mm over the northern part of the domain. This MCS developed during the Intense Observing Period (IOP) of the RELAMPAGO field campaign during Nov.~2018.

  We used the GSI-4DLETKF to produce analyses assimilating observations every hour with 10-km horizontal grid spacing and a 60-members ensemble initialized from the deterministic GFS run adding random perturbations with climatological covariance. A multiphysics approach is also used to represent model errors, using different physics configurations (a combination of PBL and convection parameterizations). We conducted four assimilation experiments using different sets of observations: CONV with conventional observations from prepBUFR, AUT that uses CONV observations plus automatic station networks, SATWND add satellite-derived winds and RAD includes satellite radiances from AMSU, HIRS, MHS, ATMS, AIRS and IASI. We found that the assimilation of observations with high temporal and spatial frequency generate an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation.
  \end{abstract}
   \begin{keyword} Regional Data Assimilation, Surface Obsevations, Satellite Observations\end{keyword}
 \end{frontmatter}

@@

DA methods can successfully be implemented by using observations with sufficient temporal and spatial resolution to characterize mesoscale atmospheric circulations.
However, surface observations, which directly measure the atmospheric state, have limited availability in South America.
Other types of observations are being assimilated with relatively high spatial and temporal resolution, such as satellite radiance observations or retrieval products.
Radiance observations particularly, are indirect measurements and are more difficult to incorporate into DA systems as they require complex forward models.

The assimilation of conventional observations from surface stations has an important role at improving the initial conditions that lead to better forecasts.
For example, Ha and Snyder (2014) showed that the assimilation of temperature and dew point temperature systematically improved the structure of the simulated planetary boundary layer that subsequently resulted in a better precipitation forecast over the U.S.

Given the sparsity of the local conventional observing network, it is important to explore the potential benefits of including additional sources of observations at a regional scale.
Previous work has shown a positive impact at incorporating temperature and humidity profiles derived from the multispectral infrared sensors (i.e.~AIRS and IASI) in a regional domain application.
Miyoshi and Kunii (2012) assimilated observations, atmospheric temperature and humidity profile data from the AIRS and found improvement on the tracking of two typhoons.
Dillon et al. (2019) also assimilated retrievals from the AIRS sensor and reported improvements on the thermodynamic variables and the regional circulation.
Moreover Bao et al. (2015) studied the impact on temperature and humidity forecast over western USA while assimilating microwave and infrared radiance data and found a reduction in the temperature bias at low and mid-levels as a result of the microwave observations but an opposite effect for infrared data. Recently Zhu et al. (2019) studied the impact of assimilating satellite radiance data within a frequently updated regional system and showed a positive improvement for all variables, in particular for relative humidity at upper levels.
Satellite-derived winds from water vapor channels and cloud drift motion vectors also have an overall positive impact on analysis and short-range forecasts (Gao et al., 2015).

@@

The model simulations for the case study were performed using the 3.9.1 version of the non-hydrostatic Advanced Research version of the Weather Research and Forecasting (WRF-ARW (V3.9), Skamarock et al. (2018)) model.
The resolution was 10 km (150 x 200 grid points) on the horizontal and 37 levels on the vertical with the top of the atmosphere at 50 hPa.
The initial and boundary conditions are provided by the Global Forecasting System (GFS) analysis (0.25\(^{\circ}\) horizontal resolution and 6 hour temporal resolution, National Centers for Environmental Prediction, National Weather Service, NOAA, U.S. Department of Commerce (2015)).
The domain covers the area indicated in Figure \ref{fig:dominio} to capture the development of the MCS during the simulated period.

@@

We use a 60-member ensemble where the ensemble mean at the beginning of the data assimilation cycle is initialized using the GFS deterministic analysis. Since the publicly available GFS ensemble members change at each cycle \textbf{(alguna fuente)} we used random perturbations to generate the initial ensemble perturbations. This method also helps to prevent an underestimation of the ensemble spread (Ouaraini et al., 2015). The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5\(^{\circ}\) horizontal grid spacing with a smooth time evolution as in Necker et al. (2020) and Maldonado et al. (2021). In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. These random perturbations are also applied at the boundaries in order to keep the ensemble spread within the domain.

@@

The conventional and satellite-derived wind observations used are part of the Global Data Assimilation System (GDAS) \textbf{{[}ver cita{]}}. We assimilated conventional observations included in the Binary Universal Form for Representation of Meteorological Data (PREPBUFR) files generated at NCEP that consist of surface observations from conventional surface weather stations (CSWS) and ships and upper-air observations from radiosondes and aircrafts. The orange triangles in Figure \ref{fig:dominio}a, are the surface stations and ship locations included in this experiment. The orange triangles in Figure \ref{fig:dominio} a), are the surface station locations included in this experiment. The frequency of these observations varied between 1 hour for surface stations and 12/24 hours for most radiosondes in the region.

@@

Satellite radiances available through the GDAS data stream, consisting of infrared and microwave observations are used in this study. This includes the Advanced Microwave Sounding Unit - A (AMSU-A), Advanced Technology Microwave Sounder (ATMS), Microwave Humidity Sounder (MHS), High-resolution Infrared Radiation Sounder (HIRS/4), and 2 multispectral sensors, Atmospheric Infrared Sounder (AIRS) and Infrared Atmospheric Sounding Interferometer (IASI) over several satellite platforms (see Table \ref{tab:table-rad}). Since the regional domain is located in the mid-latitudes and all satellite platforms are on polar orbits, each sensor scans the area only twice a day with a spatial coverage depending on the satellite swath. For this reason, the number of satellite observations varied significantly among cycles. This is evident in Figure \ref{fig:obs-cycle}a which shows the number of radiance observations assimilated at each analysis cycle as a function of pressure. In particular, the multispectral sensors provided between 100 and 10.000 observations for every scan every 12 hours, contributing 82 \% of the total amount of assimilated radiances in our experiment. The vertical location of each radiance observation was estimated as the model level at which its weighting function was maximized as calculated by CRTM. The multispectral sensors have good vertical coverage and are able to sense from the lower troposphere and up to the lower stratosphere. The channels whose maximum weighting function is located in the stratosphere were rejected due to the low model top model (50 hPa) used in the experiments.

The channels accepted for assimilation and their associated error were defined using the default GSI configuration. The data preprocessing, which is an essential step in the assimilation of radiances, was performed within the GSI system for each sensor specifically. Firstly a spatial data thinning is applied using a 60 km grid following (Jones et al., 2013; Lin et al., 2017; Singh et al., 2016), where the observations to be assimilated are chosen based on their distance to the model grid points, on the observation quality (based on available data quality information) and on the number of available channels (from the same pixel and sensor) that passed the quality control. Also, observations over the sea are preferred from those over land or snow (Hu et al., 2018).

@@

In our experiments, only clear-sky observations are used. For microwave radiances, observations potentially contaminated by clouds are detected using the scattering and Liquid Water Path (LWP) indexes (Weston et al., 2019; Zhu et al., 2016). For the infrared channels cloud contaminated observations are detected using the transmittance profile calculated within the CRTM algorithms. Additionally, the GSI quality control for infrared sensors looks for observations over water with a large zenithal angle (over 60\(^{\circ}\)) to reject channels near the visible range that can be contaminated with reflection. It also performs an emissivity check for observations over land for both infrared and microwave radiances.

@@

\begin{itemize}
\item
  The Multi-Network Composite Highest Resolution Radiosonde Data (Earth Observing Laboratory, 2020) from the RELAMPAGO field campaign database consisting of high resolution radiosondes launched from several locations during the Intensive Observation Periods (IOP) along with the operational measurements. Only the soundings that did not enter the assimilation system were used for validation. The experiment period covers IOP missions 7 and 8 during which 74 radiosondes were launched in a small area near the center of the experimental domain (Figure \ref{fig:dominio}b).
\item
  The Satellite precipitation estimation IMERG Final Run with 0.01\(^{\circ}\) spatial resolution and 30 minutes temporal resolution (Huffman et al., 2018) was used as a reference state to validate the skill of 1-hour forecasts to represent the precipitation over the domain.
\item
  Radar observations are used to perform a qualitative and visual assessment of the convection features. The data comes from 9 radars located on the domain and is provided by the Argentine C-band Doppler dual-polarization weather radar network (de Elía et al., 2017) with a temporal frequency of 10 minutes. For this work only the maximum reflectivity in the column (COLMAX) field closest to the analysis time was used.
\end{itemize}

@@

We performed all analysis in this paper using the R programming language (R Core Team, 2020), using data.table (Dowle and Srinivasan, 2020) and metR (Campitelli, 2020) packages.
All graphics are made using ggplot2 (Wickham, 2009) and the paper was rendered using knitr and rmarkdown (Allaire et al., 2019; Xie, 2015). All the experiments were performed at the National Center for Atmospheric Research (NCAR) supercomputer Cheyenne (Computational and Information Systems Laboratory, 2019).

@@

The impacts on the wind components are shown in Figure Figure \ref{fig:UV-diff} along with the corresponding averaged wind component in the experiment with the largest number of assimilated observations.

The assimilation of ASWS produces an increase of zonal wind and a decrease of meridional wind at low levels during the first two days of analysis. There is a diurnal cycle in the impact of surface weather stations on the meridional velocity (Figure \ref{fig:UV-diff}d) with a stronger reduction of the northerly wind during night hours. This indicates that surface observations are reducing the intensity of the low level jet present in the pre-convective environment. After 18 UTC Nov, 22 the opposite effect is observed when the MCS is moving through the domain. After the initiation of the convective cells the systematic impact on the wind field is larger at mid and upper levels. During Nov 22 and 23 the impact of assimilating ASWS produces an increase of northerly wind in upper levels. This could be a consequence of a stronger MCS with an increased polar side upper level outflow. Satellite-derived wind observations produce the largest impact in mid-to-upper levels where the number of observations is larger, however, the systematic impact is overall smaller than the one produced by assimilating data from ASWS.

@@

\hypertarget{verification}{%
\subsection{Verification}\label{verification}}

Firstly we analyze the impact of different observation types in terms of the representation of the MCS and its associated precipitation. Figure \ref{fig:pp-hov} shows the first-guess hourly accumulated precipitation averaged over a longitude range between 67\(^{\circ}\)W and 54.5\(^{\circ}\)W as a function of time and latitude in the different experiments, and the estimated precipitation by IMERG. The heaviest precipitation (over 12 \(mmh^{-1}\)) starts during the afternoon of Nov 22 and continues during Nov 23 after the end of the simulated period. In all the experiments, the accumulated precipitation in the short-range forecasts underestimates the precipitation. This is particularly evident on CONV where the convection initiation is significantly delayed and occurs further north with respect to the observed initiation. AUT, SATWND, and RAD better capture the timing and location of convective initiation. On RAD the initiation is delayed with respect to AUT and SATWND possibly due to the lower content of precipitable water and MCAPE on the southern tip of the moist tongue. After 18 UTC Nov, 22 RAD shows improvements in the precipitation rate and its distribution compared to the other experiments as a result of the enhanced development of the convection.

@@

To quantify the spatial match between the observed precipitation and the short-range forecasted precipitation for the different experiments, we compute the FSS in 6-hours moving windows for different thresholds and spatial scales (Figure \ref{fig:fss}). All experiments show low values of FSS before and during the initiation of the MCS around 03 UTC Nov, 22 with an improvement during the mature stage of the MCS. The FSS for CONV is the lowest compared to the rest of the experiments and the differences are larger during the mature stage of the MCS. AUT and SATWND show similar FSSs indicating that satellite-derived wind assimilation has little impact on the precipitation for the present case study. The assimilation of radiances led to an overall improvement of the 1-hour forecasted precipitation, particularly for the 25 mm threshold during the period of heaviest precipitation on Nov, 22. The enhancement is also important at the developing stage of the MCS (between 00 and 12 UTC Nov, 22 and for spatial scales above 500 km, not shown).

@@

To complement the analysis, Figure \ref{fig:dbz-mean} shows the maximum reflectivity in the column (COLMAX) for the CONV and RAD experiments ensemble mean at different times between 10 and 19 UTC Nov, 22 along with the observed maximum reflectivity. These experiments were chosen because they represent the analysis with minimum and maximum number of assimilated observations. In addition, these experiments are the worst and best performing experiments in terms of the short-range precipitation forecast skill. Overall none of the short-range forecasts is able to capture the mesoscale details in the precipitation distribution. This is partially expected considering the relatively low horizontal resolution (10 km) which is not enough to appropriately capture the strength of the convective band associated with the MCS. Also, the ensemble mean produces a smoothing effect that reduces the amplitude of local maxima in the forecasted reflectivity field. RAD better represents the observed features of the MSC showing a more strong and organized MCS over the domain center at 10 and 13 UTC (first and second columns in Figure \ref{fig:dbz-mean}). The convective cells that initiate after 16 UTC over the warm front in the northeast part of the domain are well captured by both experiments, but better represented in terms of strength in the RAD experiment. CONV captures the location of the MCS, but the convection seems to be less organized and much weaker than in RAD. Before and after the times shown in Figure \ref{fig:dbz-mean}, the agreement between experiment and observations is quite high in the regions where radar data are available.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-allaire2019}{}%
Allaire, J., Horner, J., Xie, Y., Marti, V., Porte, N., 2019. Markdown: Render markdown with the c library 'sundown'.

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis}
    \author[UBA,CIMA,CNRS]{Paola Belén Corrales\corref{1}}
   \ead{paola.corrales@cima.fcen.uba.ar} 
    \author[UBA,CIMA,CNRS]{Victoria Galligani}

@@

  \begin{abstract}
  In this paper we evaluate the impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF. We conducted a case study corresponding to a huge mesoscale convective system (MCS) developed over central and north-eastern Argentina during November 22, 2018. The accumulated precipitation associated with this MCS was quite high, exceeding 200 mm over northern Argentina and Paraguay. This MCS developed during the Intense Observing Period (IOP) of the RELAMPAGO field campaign during November 2018.

  We used the GSI-4DLETKF data assimilation package to produce analyses assimilating observations every hour with 10-km horizontal grid spacing and a 60-members ensemble initialized from the deterministic GFS run adding random perturbations with climatological covariance. A multiphysics approach is also used to represent model errors, using different physics configurations (a combination of PBL and convection parameterizations). We conducted four assimilation experiments using different sets of observations: CONV, consisting of conventional observations from NCEP's prepBUFR files, AUT combining CONV and dense automatic surface weather station networks, SATWND, combining AUT with satellite-derived winds and RAD, including SATWND and satellite radiances from different microwave and infrared sensors (AMSU, HIRS, MHS, ATMS, AIRS, and IASI). We found that the assimilation of observations with high temporal and spatial frequency generate an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed in this case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation.
  \end{abstract}
   \begin{keyword} Regional Data Assimilation, Surface Obsevations, Satellite Observations\end{keyword}
 \end{frontmatter}

@@

DA methods can successfully be implemented by using observations with sufficient temporal and spatial resolution to characterize mesoscale atmospheric circulations.
However, surface observations, which directly measure the atmospheric state, have limited availability in South America.
Other types of observations are being assimilated with relatively high spatial and temporal resolution, such as satellite radiance observations or retrieval products.
Radiance observations are indirect measurements and are more difficult to incorporate into DA systems as they require complex forward models.

The assimilation of conventional observations from surface stations has an important role in improving the initial conditions that lead to better forecasts.
For example, Ha and Snyder (2014) showed that the assimilation of temperature and dew point temperature systematically improved the structure of the simulated planetary boundary layer that subsequently resulted in a better precipitation forecast over the U.S.

Given the sparsity of the local conventional observing network, it is important to explore the potential benefits of including additional sources of observations at a regional scale.
Previous work has shown a positive impact at incorporating temperature and humidity profiles derived from the multispectral infrared sensors (i.e.~AIRS and IASI) in a regional domain application.
Miyoshi and Kunii (2012) assimilated observations, atmospheric temperature, and humidity profile data from the AIRS and found improvement on the tracking of two typhoons.
Dillon et al. (2019) also assimilated retrievals from the AIRS sensor and reported improvements on the thermodynamic variables and the regional circulation.
Moreover, Bao et al. (2015) studied the impact on temperature and humidity forecast over the western USA while assimilating microwave and infrared radiance data and found a reduction in the temperature bias at low and mid-levels as a result of the microwave observations but an opposite effect for infrared data. Recently Zhu et al. (2019) studied the impact of assimilating satellite radiance data within a frequently updated regional system and showed an improvement for all variables, in particular for relative humidity at upper levels.
Satellite-derived winds from water vapor channels and cloud drift motion vectors also have an overall positive impact on analysis and short-range forecasts (Gao et al., 2015).

@@

The model simulations for the case study were performed using the 3.9.1 version of the non-hydrostatic Advanced Research version of the Weather Research and Forecasting (WRF-ARW (V3.9), Skamarock et al. (2018)) model.
The resolution was 10 km (150 x 200 grid points) on the horizontal and 37 levels on the vertical with the top of the atmosphere at 50 hPa.
The initial and boundary conditions are provided by the Global Forecasting System (GFS) analysis (0.25\(^{\circ}\) horizontal resolution and 6-hour temporal resolution, National Centers for Environmental Prediction, National Weather Service, NOAA, U.S. Department of Commerce (2015)).
The domain covers the area indicated in Figure \ref{fig:dominio} to capture the development of the MCS during the simulated period.

@@

We use a 60-member ensemble where the ensemble mean at the beginning of the data assimilation cycle is initialized using the GFS deterministic analysis. Since the publicly available GFS ensemble members change at each cycle we used random perturbations to generate the initial ensemble perturbations. This method also helps to prevent an underestimation of the ensemble spread (Ouaraini et al., 2015). The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5\(^{\circ}\) horizontal grid spacing with a smooth time evolution as in Necker et al. (2020) and Maldonado et al. (2021). In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. These random perturbations are also applied at the boundaries to keep the ensemble spread within the domain.

@@

The conventional and satellite-derived wind observations used are part of the Global Data Assimilation System (GDAS). We assimilated conventional observations included in the Binary Universal Form for Representation of Meteorological Data (PREPBUFR) files generated at NCEP that consist of surface observations from conventional surface weather stations (CSWS) and ships and upper-air observations from radiosondes and aircraft. The orange triangles in Figure \ref{fig:dominio}a, are the surface stations and ship locations included in this experiment. The orange triangles in Figure \ref{fig:dominio} a), are the surface station locations included in this experiment. The frequency of these observations varied between 1 hour for surface stations and 12/24 hours for most radiosondes in the region.

@@

Satellite radiances available through the GDAS data stream, consisting of infrared and microwave observations are used in this study. This includes the Advanced Microwave Sounding Unit - A (AMSU-A), Advanced Technology Microwave Sounder (ATMS), Microwave Humidity Sounder (MHS), High-resolution Infrared Radiation Sounder (HIRS/4), and 2 multispectral sensors, Atmospheric Infrared Sounder (AIRS) and Infrared Atmospheric Sounding Interferometer (IASI) over several satellite platforms (see Table 2). Since the regional domain is located in the mid-latitudes and the satellite platforms of interest are on polar orbits, each sensor scans the area only twice a day with a spatial coverage depending on the satellite swath. For this reason, the number of satellite observations varied significantly among cycles. This is evident in Figure 3 a) which shows the number of radiance observations assimilated at each analysis cycle as a function of pressure. In particular, the multispectral sensors provided between 100 and 10.000 observations for every scan every 12 hours, contributing 82 \% of the total amount of assimilated radiances in our experiment. The vertical location of each radiance observation was estimated as the model level at which its weighting function was maximized as calculated by CRTM. The multispectral sensors have good vertical coverage and are able to sense from the lower troposphere and up to the lower stratosphere. The channels whose maximum weighting function is located in the stratosphere were rejected due to the low model top (50 hPa) used in the experiments.

The channels accepted for assimilation and their associated error were defined using the default GSI configuration. The data preprocessing, which is an essential step in the assimilation of radiances, was performed within the GSI system for each sensor specifically. Firstly a spatial data thinning is applied using a 60 km grid following (Jones et al., 2013; Lin et al., 2017; Singh et al., 2016), where the observations to be assimilated are chosen based on their distance to the model grid points, on the observation quality (based on available data quality information) and on the number of available channels (from the same pixel and sensor) that passed the quality control. Also, observations over the sea are preferred over those over land or snow (Hu et al., 2018).

@@

In our experiments, only clear-sky observations are used. For microwave radiances, observations potentially contaminated by clouds are detected using the scattering and Liquid Water Path (LWP) indexes (Weston et al., 2019; Zhu et al., 2016). For the infrared channels cloud contaminated observations are detected using the transmittance profile calculated within the CRTM algorithms. Additionally, the GSI quality control for infrared sensors looks for observations over water with a large zenithal angle (over 60°) to reject channels near the visible range that can be contaminated with reflection. It also performs an emissivity check for observations over land for both infrared and microwave radiances.

@@

\begin{itemize}
\item
  The Multi-Network Composite Highest Resolution Radiosonde Data (Earth Observing Laboratory, 2020) from the RELAMPAGO field campaign database consisting of high-resolution radiosondes launched from several locations during the Intensive Observation Periods (IOP) along with the operational measurements. Only the soundings that did not enter the assimilation system were used for validation. The experiment period covers IOP missions 7 and 8 during which 74 radiosondes were launched in a small area near the center of the experimental domain (Figure \ref{fig:dominio}b).
\item
  The Satellite precipitation estimation IMERG Final Run with 0.01\(^{\circ}\) spatial resolution and 30 minutes temporal resolution (Huffman et al., 2018) was used as a reference state to validate the skill of 1-hour forecasts to represent the precipitation over the domain.
\item
  Radar observations are used to perform a qualitative and visual assessment of the convection features. The data comes from 9 radars located on the domain and is provided by the Argentine C-band Doppler dual-polarization weather radar network (de Elía et al., 2017) with a temporal frequency of 10 minutes. For this work, only the maximum reflectivity in the column (COLMAX) field closest to the analysis time was used.
\end{itemize}

@@

We performed all analysis in this paper using the R programming language (R Core Team, 2020), using data.table (Dowle and Srinivasan, 2020) and metR (Campitelli, 2020) packages.
All graphics are made using ggplot2 (Wickham, 2009) and the paper was rendered using knitr and rmarkdown (Allaire et al., 2020; Xie, 2015). All the experiments were performed at the National Center for Atmospheric Research (NCAR) supercomputer Cheyenne (Computational and Information Systems Laboratory, 2019).

@@

The impacts on the wind components are shown in Figure Figure \ref{fig:UV-diff} along with the corresponding averaged wind component in the experiment with the largest number of assimilated observations. The assimilation of ASWS produces an increase of zonal wind and a decrease of meridional wind at low levels during the first two days of analysis. There is a diurnal cycle in the impact of surface weather stations on the meridional velocity (Figure \ref{fig:UV-diff}d) with a stronger reduction of the northerly wind during night hours. This indicates that surface observations are reducing the intensity of the low level jet present in the pre-convective environment. After 18 UTC Nov, 22 the opposite effect is observed when the MCS is moving through the domain. After the initiation of the convective cells, the systematic impact on the wind field is larger at mid and upper levels. During Nov 22 and 23 the impact of assimilating ASWS produces an increase of northerly wind in upper levels. This could be a consequence of a stronger MCS with an increased polar side upper level outflow. Satellite-derived wind observations produce the largest impact in mid-to-upper levels where the number of observations is larger, however, the systematic impact is overall smaller than the one produced by assimilating data from ASWS.

@@

\hypertarget{validation-against-independent-observations}{%
\subsection{Validation against independent observations}\label{validation-against-independent-observations}}

Firstly we analyze the impact of different observation types in terms of the representation of the MCS and its associated precipitation. Figure \ref{fig:pp-hov} shows the first-guess hourly accumulated precipitation averaged over a longitude range between 67\(^{\circ}\)W and 54.5\(^{\circ}\)W as a function of time and latitude in the different experiments, and the estimated precipitation by IMERG. The heaviest precipitation (over 12 \(mmh^{-1}\)) starts during the afternoon of Nov 22 and continues during Nov 23 after the end of the simulated period. In all the experiments, the accumulated precipitation in the short-range forecasts underestimates the precipitation. This is particularly evident on CONV where the convection initiation is significantly delayed and occurs further north with respect to the observed initiation. AUT, SATWND, and RAD better capture the timing and location of convective initiation. On RAD the initiation is delayed when we compare with AUT and SATWND possibly due to the lower content of precipitable water and MCAPE on the southern tip of the moist tongue. After 18 UTC Nov, 22 RAD shows improvements in the precipitation rate and its distribution compared to the other experiments as a result of the enhanced development of the convection.

@@

To quantify the spatial match between the observed precipitation and the short-range forecasted precipitation for the different experiments, we compute the FSS in 6-hours moving windows for different thresholds and spatial scales (Figure \ref{fig:fss}). All experiments show low values of FSS before and during the initiation of the MCS around 03 UTC Nov, 22, with an improvement during the mature stage of the MCS. The FSS for CONV is the lowest compared to the rest of the experiments and the differences are larger during the mature stage of the MCS. AUT and SATWND show similar FSSs indicating that satellite-derived wind assimilation has little impact on the precipitation for the present case study. The assimilation of radiances led to an overall improvement of the 1-hour forecasted precipitation, particularly for the 25 mm threshold during the period of heaviest precipitation on Nov, 22. The enhancement is also important at the developing stage of the MCS (between 00 and 12 UTC Nov, 22 and for spatial scales above 500 km, not shown).

@@

To complement the analysis, Figure \ref{fig:dbz-mean} shows the maximum reflectivity in the column (COLMAX) for the CONV and RAD experiments ensemble mean at different times between 10 and 19 UTC Nov, 22th along with the observed maximum reflectivity. These experiments were chosen because they represent the analysis with the minimum and the maximum number of assimilated observations. In addition, these experiments are the worst and best performing experiments in terms of the short-range precipitation forecast skill. Overall none of the short-range forecasts is able to capture the mesoscale details in the precipitation distribution. This is partially expected considering the relatively low horizontal resolution (10 km) which is not enough to appropriately capture the strength of the convective band associated with the MCS. Also, the ensemble mean produces a smoothing effect that reduces the amplitude of local maxima in the forecasted reflectivity field. RAD better represents the observed features of the MSC showing a more strong and organized MCS over the domain center at 10 and 13 UTC (first and second columns in Figure \ref{fig:dbz-mean}). The convective cells that initiate after 16 UTC over the warm front in the northeast part of the domain are well captured by both experiments, but better represented in terms of strength in the RAD experiment. CONV captures the location of the MCS, but the convection seems to be less organized and much weaker than in RAD. Before and after the times shown in Figure \ref{fig:dbz-mean}, the agreement between experiment and observations is quite high in the regions where radar data are available.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-allaire2020}{}%
Allaire, J.J., Xie {[}aut, Y., cre, McPherson, J., Luraschi, J., Ushey, K., Atkins, A., Wickham, H., Cheng, J., Chang, W., Iannone, R., Dunning, A., filter), A.Y.(. sections L., Schloerke, B., Dervieux, C., Aust, F., Allen, J., Seo, J., Barrett, M., Hyndman, R., Lesur, R., Storey, R., Arslan, R., Oller, S., RStudio, PBC, library), j.F.(., inst/rmd/h/jquery-AUTHORS.txt), j. contributors (. library; authors listed in, inst/rmd/h/jqueryui-AUTHORS.txt), j.U. contributors (.U. library; authors listed in, library), M.O.(., library), J.T.(., library), B. contributors (., Twitter, library), I.(., library), A.F.(., library), S.J.(. js, library), I.S.(. js, library), G.F.(., templates), J.M.(., Google, library), I.(., library), D.R.(., library), W.(., Gandy (Font-Awesome), D., Sperry (Ionicons), B., (Ionicons), D., StickyTabs), A.L.(., filter), B.P.J.(.L., filter), A.K.(.L., 2020. Rmarkdown: Dynamic Documents for R.
